Dependent Object Types

### 2012-08-09 article.tex
forward ref to pres-patch
references

@@

\section{The DOT Calculus}\label{pres}

@@

@@

\subsubsection{Why not patch the DOT calculus for preservation to hold?}

@@

>>>>

%The primary contributions of this paper are:
%\begin{itemize}
%\item Development of DOT -- a core calculus which models
%  path-dependent types. We formally specify a small-step operational
%  semantics and a static typing assignment in
%  section~\ref{dot-calculus} and show some examples in
%  section~\ref{dot-examples}.
%\item Counterexamples to the standard theorem of preservation --
%  section~\ref{dot-preservation}.
%\item A sketch of a type-safety proof based on logical relations --
%  section~\ref{dot-type-safety}.
%\end{itemize}

@@

\section{The DOT Calculus}\label{dot-calculus}

@@

In section~\ref{pres-patch}, we discuss our failure to patch the
calculus for preservation to hold.

@@

\subsubsection{Why not patch the DOT calculus for preservation to hold?}\label{pres-patch}

@@

\subsection{Related Work}

In addition to Scala's previous models~\cite{nuObj,FS}, several
calculi present some form of path-dependent types.

The {\it vc} calculus~\cite{vc} models virtual classes with
path-dependent types. {\it vc} restricts paths to start with ``this'',
though it provides a way (``out'') to refer to the enclosing object.

The Tribe calculus~\cite{tribe} builds an ownership types
system~\cite{tribalo} on top of a core calculus which models virtual
classes. The soundness proof for the core calculus seems to be tied to
the ownership types system.

Some ML-style module systems~\cite{homl,mixinml} have a form of
stratified path-dependent types. Because of the stratification,
recursion is not allowed. In MixML~\cite{mixml} like in Scala, this
restriction is lifted.
